---
title: "msTrawler: Accounting for the properties of low signal intensities in the modeling of multiplexed proteomics experiments"
author: Jonathon O'Brien
output: 
  html_document:
    toc: true
    number_sections: true
    theme: united
vignette: >
  %\VignetteIndexEntry{msTrawler_Manual}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Topline Header requires no notation?

# Pre-processing Steps

## Limit of Detection (LOD)

Function Description: tmtLOD The tmtLOD function is used for imputing missing values in a matrix of signal-to-noise ratios and a matrix of intensities.
It takes three main arguments: snMat, a matrix of signal-to-noise ratios with channels in the columns and scans in each row; iMat, a matrix of intensities with channels in the columns and scans in each row; and lod, a value that determines the limit of reliability.
The threshold will be a proportion of the total scan intensity if the value is between zero and one.
If lod \>= 1, then the threshold will be set at a SNR = lod for all scans.

Input Parameters The input parameters for the tmtLOD function are as follows:

snMat: a matrix of signal-to-noise ratios with channels in the columns and scans in each row.
iMat: a matrix of intensities with channels in the columns and scans in each row.
lod: a value that determines the limit of reliability.
If the value is between zero and one, then the threshold will be a proportion of the total scan intensity.
If lod \>= 1, then the threshold will be set at a SNR = lod for all scans.
minAbove: an integer value that represents the minimum number of observations above the lod threshold that a scan must have in order to not be flagged as too few.
scaleSN: a numeric value used to scale the standard deviation of the imputed values.
imputePenalty: a numeric value used to adjust the penalty function used for imputing missing values.
Output Parameters The output of the tmtLOD function is a length three list.
The first component has a matrix of post-imputation intensities, and the second has the post-imputation SNRs.
The final component contains an indicator variable for flagging scans with too few observations above the lod threshold (as determined by minAbove).

Algorithm The tmtLOD function uses the following algorithm:

Calculate aggregate measures that will be used to find a threshold, including the total signal-to-noise ratio and total intensity for each scan, as well as a matrix of proportions of intensities for each scan.
Figure out which values will be censored (i.e., imputed) by creating a boolean matrix censoredB based on whether the proportions of intensities are below the lod threshold.
If lod \< 1, then the censoredB matrix is calculated based on proportions of intensities; otherwise, it is calculated based on SNRs.
Also, create a vector of indices censoredI of the elements in iMat and snMat that are below the lod threshold.
Check for scans with too few observations above the lod threshold by creating a boolean vector tooFew, which is set to TRUE if a scan has fewer than minAbove observations above the lod threshold.
Calculate relevant thresholds for imputing missing values based on the lod value.
If lod \< 1, then thresholds can be found independently for SNRs and intensities; otherwise, the SN limit can be converted to an intensity by matching rank-ordered observations.
Generate imputed values using a log-normal distribution with a mean of half the relevant threshold and a standard deviation scaled by the scaleSN parameter.
Update the iMat and snMat matrices with the

## Outlier Removal

Standard stuff.
Works OK. The interesting piece is the possibility of keeping the outliers but removing them from protein groups.

## Global Sample Adjustments

Function Description: geoNorm The geoNorm function performs global column adjustments on a matrix of reporter ion intensities.
It takes four input arguments: mat, a matrix of reporter ion intensities that need to be adjusted; normIndex, a boolean vector with length equal to the number of rows in mat, indicating which rows will be used to calculate the normalization factors; Plex, a vector denoting plex membership, which determines how many adjustments will be made; and ratios, a numeric vector with length equal to the number of normalization factors, which determines the expected relationship between all of the columns.

The function returns a list with two components.
The first component is a matrix that has been adjusted so that the geometric mean of the subset of rows specified by normIndex will be equivalent across all columns.
The second list component contains a vector with all the log additive values used to adjust each column.

Input Parameters The input parameters for the geoNorm function are as follows:

mat: a matrix of reporter ion intensities that need to be adjusted.
normIndex: a boolean vector with length equal to the number of rows in mat.
Each TRUE indicates that the corresponding row will be used to calculate the normalization factors.
Plex: a vector denoting plex membership.
Normalization factors are computed for every channel\*plex combination.
Accordingly, this variable determines how many adjustments will be made.
ratios: a numeric vector with length equal to the number of normalization factors.
The ratios in this vector determine the expected relationship between all of the columns.
Output Parameters The output of the geoNorm function is a list with two components:

The first component is a matrix that has been adjusted so that the geometric mean of the subset of rows specified by normIndex will be equivalent across all columns.
The second list component contains a vector with all the log additive values used to adjust each column.
Algorithm The geoNorm function uses the following algorithm to perform global column adjustments:

Replace any 0 values in the input mat matrix with NA values, since log2(0) is undefined.
Take the logarithm (base 2) of the input mat matrix and store the result in a new matrix called lMat.
Get a vector of unique plex membership values (uPlex) from the Plex input vector.
Calculate the mean of the lMat matrix for each unique plex membership value (chMeans) using the rows specified by the normIndex input vector.
Calculate the grand mean of the chMeans vector minus the log2(ratios) vector to get the log additive value that will be used to adjust each column (grandMean).
Subtract log2(ratios) and grandMean from chMeans to get the normalization factors (normFactors) for each unique plex membership value.
If there is more than one unique plex membership value, rename the columns of the normFactors matrix with the corresponding plex membership value.
Adjust each channel*plex combination of the lMat matrix by subtracting the corresponding normalization factors and then exponentiate each element. Store the result in a list called normed. Update the input mat matrix with the normalized values in the normed list, by replacing the original values with the normalized values for each channel*plex combination.
Return a list with the updated mat matrix as the first component and the normFactors matrix as the second component.

title: "Remove consensus outliers from protein groupings" output: html_document {r Copy code knitr::opts_chunk\$set(echo = TRUE) Overview The findOutliers function removes consensus outliers from protein groupings by fitting two linear models to the data and identifying entries that meet the definition of an outlier.
The first model fits the average profile without an intercept, while the second model fits with an intercept.
The function then calculates the standardized residuals for both models and identifies outliers based on the absolute value of these residuals.
Entries are considered outliers if they meet the outlier criteria for either model.
The function returns a matrix of boolean values indicating which entries are considered outliers.

#findOutliers Function parameters The findOutliers function has the following parameters:

protMat: A matrix of reporter ion intensities from a single protein.
snMat: A matrix of signal-to-noise values for the reporter ions.
outlierCutoff: Numeric value specifying the cutoff for defining an outlier based on the absolute value of standardized residuals (default: 3).
scaleSN: Scaling factor for the signal-to-noise values in the linear model (default: 1).
Return value The function returns a matrix of boolean values indicating which entries meet the definition of an outlier.

Example {r} Copy code \# Load data \# protMat \<- your_protein_matrix \# snMat \<- your_sn_matrix

# Find outliers

# outliers \<- findOutliers(protMat, snMat)

See also msTrawl: A function for processing and analyzing mass spectrometry data.
# Statistical Modeling

## The full hypothetical model for protein abundance measurments

## Bridge Channels and the Statistical Blocking of Scan IDs

### What if we don't have a bridge channel?

# Output Files and

### Now for the really weak stuff

```{r}
1+1
```
