---
title: "msTrawler: Accounting for the properties of low signal intensities in the modeling of multiplexed proteomics experiments"
author: Jonathon O'Brien
output: 
  html_document:
    toc: true
    number_sections: true
    theme: united
vignette: >
  %\VignetteIndexEntry{msTrawler_Manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Topline Header requires no notation?
---

# Pre-processing Steps

## Limit of Detection (LOD)
TMT creates a phantom LOD.  This is crazy.  We did something cool.

## Outlier Removal
Standard stuff.  Works OK.  The interesting piece is the possibility of keeping the outliers but removing them from protein groups.

## Global Sample Adjustments
Turns out we don't want to use all measurements when aligning the columns.

# Statistical Modeling

## The full hypothetical model for protein abundance measurments

## Bridge Channels and the Statistical Blocking of Scan IDs



### What if we don't have a bridge channel?

# Output Files and 

### Now for the really weak stuff

```{r}
1+1
```

